Group 5 Report

### 2022-08-01 Report/Group 5 report.Rmd
edit limitations
Setting out.width = "100%" and pdf as default.

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "`r Sys.Date()`"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE)
```

@@

```{r}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r}
knitr::include_graphics("Images/info_kreft.png")
knitr::include_graphics("Images/regnskapssti.png")
```

>>>>

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, out.width = "100%")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r, echo=FALSE}
knitr::include_graphics("Images/info_kreft.png")
knitr::include_graphics("Images/regnskapssti.png")
```
